---
title: "Report Cards Table Data Dictionary"
author: "Spencer Schien"
date: "4/7/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
library(wisconsink12)
library(tidyverse)
library(knitr)
```

## Description

The `report_cards` table contains data made available through DPI's [School Report Card Data Download Files](https://apps2.dpi.wi.gov/reportcards/).  A few manipulations have been performed on the data to facilitate analysis:

* Variable names have been cleaned so they are shorter, they include only lower case characters, and they have no spaces
* District and school codes have been replaced by the `dpi_true_id` variable, which standardizes the codes across the years (even if codes didn't change, the padding of codes was not consistent in DPI's reports, where a code might be 400 one year and 0400 another)
* Many variables in DPI's report have been removed because they are superfluous (e.g. state comparison scores)
* Two columns have been added to facilitate filters -- these are the `cg_redacted` (i.e. Closing Gaps is redacted in 2019-20) and `has_2_rc` (i.e. Choice school has two report cards for the given year)

## Dictionary

The table below contains the data dictionary for the `report_cards` table.  This dictionary is also provided in CSV form in this folder ([raw here](https://raw.githubusercontent.com/cityforwardcollective/wi_schools/master/data_dictionaries/report_cards/report_cards_data_dictionary.csv)).

```{r report_cards_dictionary}
dict <- read_csv("report_cards_data_dictionary.csv")

dict %>%
  kable(booktabs = T)
```